### 2020-04-22 final_report/methodology.tex
refer to NNs as ANNs

In our experiments, we evaluate and compare surrogates in effort to
optimise against metrics described in~\cref{sec:metrics}. To attain meaningful
and practically usable results, we require a sufficiently large and diverse pool
of surrogate classes to draw from. This is described by the listing in~\cref{tbl:surrogates}. The presented selection of models includes basic
techniques suitable for linear regression enhanced by the kernel trick or dimension
lifting, methods driven by decision trees, instance-based learning models,
ensemble regressors, randomized algorithms, neural networks and mathematical approaches
developed specifically for the purposes of surrogate modelling. For each of
these classes, a state-of-the-art implementation was selected and adapted to
operate with TBR samples.

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llll}
		\toprule
		Surrogate & Acronym & Implementation & Hyperparameters \\
		\midrule
		Support vector machines	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
		Gradient boosted trees	& GBT & SciKit Learn & 11 \\
		Extremely randomized trees	& ERT & SciKit Learn & 7 \\
		AdaBoosted decision trees	& AB & SciKit Learn & 3 \\
		Gaussian process regression	& GPR & SciKit Learn & 2 \\
		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
		Neural networks	& NN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
		Inverse distance weighing & IDW & SMT~\cite{SMT2019} & 1 \\
		Radial basis functions & RBF & SMT & 3 \\
		Stochastic gradient descent & SGD & SciKit Learn & 13 \\
		Ridge regression & RR & SciKit Learn & 4 \\
		Kriging & KRG & SMT & 4 \\
		\bottomrule
		\end{tabular}
	}
	\caption{Considered surrogate model classes.}
	\label{tbl:surrogates}
\end{table}

>>>>

In our experiments, we evaluate and compare surrogates in effort to
optimise against metrics described in~\cref{sec:metrics}. To attain meaningful
and practically usable results, we require a sufficiently large and diverse pool
of surrogate classes to draw from. This is described by the listing in~\cref{tbl:surrogates}. The presented selection of models includes basic
techniques suitable for linear regression enhanced by the kernel trick or dimension
lifting, methods driven by decision trees, instance-based learning models,
ensemble regressors, randomized algorithms, artificial neural networks and mathematical approaches
developed specifically for the purposes of surrogate modelling. For each of
these classes, a state-of-the-art implementation was selected and adapted to
operate with TBR samples.

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llll}
		\toprule
		Surrogate & Acronym & Implementation & Hyperparameters \\
		\midrule
		Support vector machines	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
		Gradient boosted trees	& GBT & SciKit Learn & 11 \\
		Extremely randomized trees	& ERT & SciKit Learn & 7 \\
		AdaBoosted decision trees	& AB & SciKit Learn & 3 \\
		Gaussian process regression	& GPR & SciKit Learn & 2 \\
		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
		Artificial neural networks	& ANN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
		Inverse distance weighing & IDW & SMT~\cite{SMT2019} & 1 \\
		Radial basis functions & RBF & SMT & 3 \\
		Stochastic gradient descent & SGD & SciKit Learn & 13 \\
		Ridge regression & RR & SciKit Learn & 4 \\
		Kriging & KRG & SMT & 4 \\
		\bottomrule
		\end{tabular}
	}
	\caption{Considered surrogate model classes.}
	\label{tbl:surrogates}
\end{table}

### 2020-04-22 final_report/results.tex
refer to NNs as ANNs

The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
experiment, gradient boosted trees clearly appear to be the most accurate as
well as the fastest surrogate class in terms of mean prediction time. Following
that, we note that extremely randomised trees, support vector machines and
neural networks also achieved satisfactory results with respect to both examined metrics.
While the remainder of tested surrogate classes does not exhibit problems in
complexity, its regression performance falls below average.

@@

In the next experiment we examine surrogate scaling properties correlating
metrics of interest with progressively increasing training set size. The results
shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
methods based on decision trees and neural networks offer the best accuracy on
larger sets overall. This is a curious extension of the previous findings, where
gradient boosted trees were observed to significantly dominate over the rest of
the examined methods. With increasing training set size, their relative advantage is
clearly gradually diminished.

@@

According to our experiment, the lowest mean training time is generally achieved
by instance-based learning methods, which seem to offer near-constant scaling
characteristics at the expense of significant performance increase later during
prediction. Following that, we observe that the majority of tree-based methods also exhibit
desirable properties. The notable exception here appear to be neural networks,
which are the only model to utilise parallelisation. As such, their constant
synchronisation overhead presumably hinders performance on small training sets,
producing misleading results when divided by the number of samples.

>>>>

The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
experiment, gradient boosted trees clearly appear to be the most accurate as
well as the fastest surrogate class in terms of mean prediction time. Following
that, we note that extremely randomised trees, support vector machines and
artificial neural networks also achieved satisfactory results with respect to both examined metrics.
While the remainder of tested surrogate classes does not exhibit problems in
complexity, its regression performance falls below average.

@@

In the next experiment we examine surrogate scaling properties correlating
metrics of interest with progressively increasing training set size. The results
shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
methods based on decision trees and artificial neural networks offer the best accuracy on
larger sets overall. This is a curious extension of the previous findings, where
gradient boosted trees were observed to significantly dominate over the rest of
the examined methods. With increasing training set size, their relative advantage is
clearly gradually diminished.

@@

According to our experiment, the lowest mean training time is generally achieved
by instance-based learning methods, which seem to offer near-constant scaling
characteristics at the expense of significant performance increase later during
prediction. Following that, we observe that the majority of tree-based methods also exhibit
desirable properties. The notable exception here appear to be artificial neural networks,
which are the only model to utilise parallelisation. As such, their constant
synchronisation overhead presumably hinders performance on small training sets,
producing misleading results when divided by the number of samples.
